### 2011-02-10 paper/results.tex
foo

The results for the parameterized gaits are shown in
\figref{std_error} and \tabref{results}.  As a group, these strategies
produced results not significantly better than the randomly-generated
gaits, however, all methods managed to explore the space enough to
significantly improve on the previous hand coded gait in at least one
of the three runs.  No single strategy consistently outperformed the
others: for the first trial Linear Regression produced the fastest
gait at 27.58 body lengths/minute, for the second a random gait
actually won with 17.26 body lengths/minute, and for the third trial
the Nelder-Mead simplex method attained the fastest gait at 14.83 body
lengths/minute.

>>>>

The results for the parameterized gaits are shown in
\figref{std_error} and \tabref{results}.  As a group, these strategies
produced results equal to or worse not significantly better than the randomly-generated
gaits, however, all methods managed to explore the space enough to
significantly improve on the previous hand coded gait in at least one
of the three runs.  No single strategy consistently outperformed the
others: for the first trial Linear Regression produced the fastest
gait at 27.58 body lengths/minute, for the second a random gait
actually won with 17.26 body lengths/minute, and for the third trial
the Nelder-Mead simplex method attained the fastest gait at 14.83 body
lengths/minute.
